Predicting Covid Data

### 2022-12-05 main.rmd
Updated meeting changes

## Introduction

- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
- They then use the function to approximate the number of cumulative positive cases in Italy
- Then performed 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
- This study does not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc. 
=======
## The Monte Carlo Study:

@@

* Mathematical prediction of the time evolution of the COVID-19 pandemic by a Gauss error function and Monte Carlo simulations:
  * The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function: $a+b*erf(c*x-d)$.
  * Predicted the potential number of cases in Italy.
  * Predicted the day in which the peak of the number of daily cases in Italy occurs.

@@

# Monte Carlo Simulations

## China

## Italy

## Australia

>>>>

## The Monte Carlo Study:

@@

* The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function: $a+b*erf(c*x-d)$.
* Predicted the potential number of cases in Italy.
* Predicted the day in which the peak of the number of daily cases in Italy occurs.

@@
